Understanding domestic abuse - Pathways to Impact

### 2019-07-30 pathways_to_impact.tex
N minor edits to pathways to impact
Update pathways_to_impact.tex

Our pathway to impact is built upon the strong existing relationships we have with West Midlands Police (WMP), and the College of Policing (CoP). These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing.

@@

3. The programme on ``police mis-recording of abuse'', is of direct interest to their data quality and reporting, as well as identifying any potential shortcomings in the way they deal with reports from particular types of victims.

@@

We will contact, in the first three months of project, domestic abuse charities including Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis.

In the second year of the proposal, we will hold a 1-day impact summit at Warwick Business School's London Shard venue. This will be funded by the Warwick Business School Impact Fund, and potentially the ESRC Impact Acceleration Account. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry, and key contacts from the third sector agencies. The summit will be a 50/50 academic and practitioner mix. Although a high-profile dissemination event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.

In addition to the academic journal outputs, we will present the findings in a series of thought leadership pieces for dissemination across the police and third-sector contacts. We will submit these reports to the CoP What Works database and log them on the \href{https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx}{Research Map}.

@@

PI Mullett will spend half of his time of the project leading the impact activity and takes overall responsibility of delivering the impact programme. Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority. CI Stewart will also spend half of his time of the project on the impact activity. Stewart has significant experience of impact activities in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association. Postdoc Trendl will be fully involved in the impact programme. This is an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts.

We will apply to the Warwick ESRC Impact Acceleration Account and to Warwick Business School Impact Fund and continue the impact programme beyond the end of the funded period.

>>>>

Our pathway to impact is built upon the strong existing relationships we have with West Midlands Police (WMP), and the College of Policing (CoP). These existing relationships are complemented by our membership of the University of Warwick's Centre for Operational Policing Research (COPR), which provides access to an even wider established network within UK policing. Our model for impact is to have a senior-level sponsor and a day-to-day contact with each organisation we work with. Impact is only delivered by understanding the policy and operational concerns of each organisation and translating the research into direct actions within the organisation.

@@

3. The programme on ``police mis-recording of abuse'', is of direct interest to their data quality and reporting, as well as identifying any potential shortcomings in the way they deal with reports from particular types of victims. It is of particular importance to victims, as mis-reporting can result in them being directed to the wrong support systems, which are not appropriate for their needs.

@@

We will contact, in the first three months of project, domestic abuse charities including Women's Aid, Refuge, Safe Lives, and National Centre for Domestic Abuse, and visit them at their offices to present the programme of research and involve them as we conduct the initial analysis. We will then follow up with these organisations at the end of the grant to present our overall conclusions and discuss how these can be most useful to the organisations' aims.

In the second year of the proposal, we will hold a 1-day impact summit at Warwick Business School's London Shard venue, and subsequently publish a summary including policy briefing notes. This will be funded by the Warwick Business School Impact Fund. We will host the National Police Chiefs' Council lead for Domestic Abuse, Deputy Chief Constable Louisa Rolfe (who is also at WMP), and Members of Parliament from the Home Affairs Committee domestic abuse inquiry, and key contacts from the third sector agencies. The summit will be a 50/50 academic and practitioner mix. Although a high-profile dissemination event at the Shard will attract attention, it is the continuous week-on-week contact with our impact partners that we think will deliver the legacy impact for this project.

In addition to the academic journal outputs, we will present the findings in a series of thought leadership pieces for dissemination across the police and third-sector contacts. We will submit these reports to the CoP What Works database and log them on the \href{https://whatworks.college.police.uk/Research/Research-Map/Pages/Research-Map.aspx}{Research Map}. These thought leadership pieces, as well as our other impact pathways will allow us to feed our results into the next Violence Against Women and Girls (VAWG) Strategy. The current strategy covers 2016 - 2020 \cite{vawag}, meaning we will be well placed to feed our results into the early stages of the subsequent strategy update. A primary goal of the 2016 - 2020 strategy is to identify victims at the earliest possible opportunity to prevent violence and abuse from escalating. Our results will be directly applicable to measuring success on this goal, and providing future direction.

@@

PI Mullett will spend half of his time on the project leading the impact activity and takes overall responsibility of delivering the impact programme. Mullett has worked extensively on the impact programme from the ESRC funded ``Accumulating to Choose'' programme, with the Financial Conduct Authority. CI Stewart will also spend half of his time of the project on the impact activity. Stewart has significant experience of impact activities in the domain of financial decision making with Lloyds Banking Group, Barclays Bank, and the UK Finance Association. Postdoc Trendl will be fully involved in the impact programme. This is an important part of the professional development for an early career researcher, and will allow her to establish a network of independent contacts.

Warwick Business School's commitment of a 4 year PhD studentship to run beyond the end of the current project will allow us to continue impact activities into the future. To further support this impact activity beyond the end date of the current grant we will also utilize the Warwick Business School Impact Fund, and apply for funds from other sources. Future work will allow us to direct research questions towards the areas identified in this project, and in collaboration with our impact partners.
